data_cleaning_longer_period

### 2023-08-15 code/analysis_Redo.Rmd
mid session updates
lots of new code

>>>>

# Redo the analysis

did2s(
      data = dfc %>% 
        select(ID, Year, Tx, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate, closed) %>% 
        mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               quick_ratio = as.numeric(quick_ratio),
               fringe_rate = as.numeric(fringe_rate)) %>% 
        inner_join(dfc %>% filter(Year == 2010) #& Total > 20000) 
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "closed", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

event_study(data = dfc %>% mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate) / 6), 
  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)

### 2023-08-15 code/data_cleaning_longer.Rmd
lots of new code

@@

## Remove some weird shit in CT
df.comp <- df.comp %>% 
  filter(BHCMISID != "01E00010") %>%  #%>%  filter(STATE != 'CT')
select(BHCMISID:FIPS, ID, Total:Pct.COM, imm.rate:MinYear)

@@

sites.in.zips <- uds.sites.full %>% 
  filter(Year >= included.years[1]) %>% 
  group_by(`BHCMIS ID`, Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  pivot_wider(id_cols = c(Zip, `BHCMIS ID`), names_from = Year, values_from = Counts) %>% 
  pivot_longer(cols = `2010`:`2021`) %>% 
  mutate(value = ifelse(is.na(value), 0, value)) %>% 
  arrange(Zip, name)

clinics.in.zips <- uds.sites.full %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  pivot_wider(id_cols = c(Zip), names_from = Year, values_from = Counts) %>% 
  pivot_longer(cols = `2011`:`2017`) %>% 
  mutate(value = ifelse(is.na(value), 0, value)) %>% 
  arrange(Zip, name)

sites.in.zips %>% 
  left_join(clinics.in.zips, by = c("Zip","name"))%>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(Clinics = max(Clinics)) 
```

## Write the file
```{r}
#write_csv(df.comp, file = "/Users/jhm65/Dropbox/Projects/Competition/data_processed/analyticalfile.csv")

@@

>>>>

## Set study period
```{r}

@@

## Remove some weird shit in CT
df.comp <- df.comp %>% 
  filter(BHCMISID != "01E00010") %>%  #%>%  filter(STATE != 'CT')
select(BHCMISID:FIPS, Total:Pct.COM, imm.rate:MinYear)

@@

clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  filter(Year >= included.years[1]) %>% 
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
  arrange(desc(Clinics))

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1 & `2012` == 1) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

# Classify clinics by introduction of competition
comp.initial <- clinics.comp %>%  #left_join(clinics.comp %>% mutate(Year = as.numeric(name)), uds.zip.totals, by = c("BHCMIS ID", "name" = "Reporting Year")) %>% 
  mutate(Year = as.numeric(name)) %>% 
  left_join(uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
              filter(Year >= included.years[1]) %>%
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Sites = n()), by = c("BHCMIS ID","Year")) %>% 
  ungroup() %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Att = min(ifelse(Tx == 0, 2, 1)*Year, na.rm = TRUE) ) %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Att = ifelse(Att < 2022, Att, 0)) %>% 
  ungroup() %>% 
  mutate(ID = as.numeric(factor(`BHCMIS ID`)))

# Expandors vs Expandees
comp.initial <- comp.initial %>% 
  left_join(
      left_join(comp.initial %>% select(`BHCMIS ID`, Att) %>% unique(), uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
                  filter(Year >= included.years[1]) %>%
        select(`BHCMIS ID`, Zip, Year) %>% 
        group_by(`BHCMIS ID`, Zip) %>% 
        summarise(YearFirstInZip = min(Year)) %>% 
        filter(YearFirstInZip %notin% c(2010)) %>% 
        select(`BHCMIS ID`, YearFirstInZip) %>% 
        unique(), by = c("BHCMIS ID")) %>% #filter(`BHCMIS ID` == "H80CS00101") %>% 
        mutate(Expandor = ifelse(is.na(YearFirstInZip) | Att != YearFirstInZip, 0, 1)) %>%  #  is.na(YearFirstInZip) | Att != YearFirstInZip
        group_by(`BHCMIS ID`) %>% summarise(Expandor = max(Expandor)), by = c("BHCMIS ID")) %>% filter(Expandor == 0)

dfc <- comp.initial %>% 
  left_join(df.comp, by = c("BHCMIS ID" = "BHCMISID", "Year"))
```

## Finalize the core set of measures
```{r}

dfc %>% 
  mutate(Liabilities = `Liabilities (as pct of assets)` * `Total net assets`, 
         Staffing = `Total expenses before depreciation` * Personnel, 
         LBE.pct = `Gross land, buildings and equipment (LBE)` / `Total net assets`, 
         `Liabilities (as pct of assets)` = `Liabilities (as pct of assets)` * 100, 
         `Surplus as a pct of before dep expenses` = `Surplus as a pct of before dep expenses` * 100, 
         Qcomp = (pap.rate + crc.rate + asthma.rate + cad.rate + ivd.rate + childbmi.rate + adultbmi.rate) / 7, 
         CostOfCare = `Total expenses before depreciation` / Total) %>%

  mutate(Liquidity =  `Total net assets` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
         Profitability =  `Unrestricted surplus (deficit) before depreciation` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
         Efficiency = (`Total revenue (unrestricted & restricted)` - `Total expenses before depreciation`) / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
         NetWorth = (100 - `Liabilities (as pct of assets)`) / `Liabilities (as pct of assets)` / 100) %>% 
  mutate(Altmans.Z = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% # 6.56, 3.26, 6.72, 1.05  OR 0.18, 0.3, 0.81, 0.14
  mutate(Liquidity = ifelse(Liquidity == 'Inf', NA, Liquidity), 
         Profitability = ifelse(Profitability == 'Inf', NA, Profitability), 
         Efficiency = ifelse(Efficiency == 'Inf', NA, Efficiency), 
         NetWorth = ifelse(NetWorth == 'Inf', NA, NetWorth), 
         Altmans.Z = ifelse(Altmans.Z == 'Inf', NA, Altmans.Z))

@@

## Write the file
```{r}
#write_csv(dfc, file = "/Users/jhm65/Dropbox/Projects/Competition/data_processed/analyticalfile.csv")
